Syntax Is All You Need: A Universal-Language Approach to Mutant Generation

### 2023-09-27 paper/main.tex
explain

One obvious concern with any-language source-based mutation is that every time the
program changes, the cost of invalid mutants must be paid again.
However, the locality of mutants and source changes in fact means this
is seldom required.   Because a mutant is asmall source change, updating a mutant to
reflect even large changes to a source file is nearly cost-free, and if the
original mutant was valid, the new mutant will usually also be valid.
New mutant generation is only required for new lines of code and
modified lines of code.  Our
implementation allows the use of the {\tt git merge-file} algorithm to control the
modification of most mutants, and uses our mechanism for
selective mutant generation to force mutation where
there is a conflict in a ``mutant patch.''

@@

The number of valid mutants is usually
slightly smaller for Comby, but Comby actually produces a larger mean
(but not median) number of mutants for Rust, due to one project where
Comby produces a much larger number of valid mutants.  As discussed
below, mutation scores and mutant equivalence rates are similar for
both modes.

On Python, TCE on Python bytecode was possible. The
number of redundant (equivalent to the original bytecode, or
the bytecode of an already-generated mutant) mutants was
overall similar for both Regex and Comby, though varied widely by file.

>>>>

One concern with our approach is that every time the
program changes, the cost of invalid mutants must be paid again.
However, the locality of mutants and source changes in fact means this
is seldom required.   Because a mutant is asmall source change, updating a mutant to
reflect even large changes to a source file is nearly cost-free, and if the
original mutant was valid, the new mutant will usually also be valid.
New mutant generation is only required for new lines of code and
modified lines of code.  Our
implementation allows the use of the {\tt git merge-file} algorithm to control the
modification of most mutants, and uses our mechanism for
selective mutant generation to force mutation where
there is a conflict in a ``mutant patch.''

@@

The number of valid mutants is usually
slightly smaller for Comby, but Comby actually produces a larger mean
(but not median) number of mutants for Rust, due to one project where
Comby produces a much larger number of valid mutants.  The small gain
in valid mutants for Regexp is partly due to Regexp (unfortunately)
mutating some comments, and partly due to a reported, but not yet
fixed, bug in Comby's handling of an operator swapping items in
literal lists.  As discussed
below, mutation scores and mutant equivalence rates are similar for
both modes.

For Python, TCE on Python bytecode was possible. The
number of redundant (equivalent to the original bytecode, or
the bytecode of an already-generated mutant) mutants was
overall similar for both Regex and Comby, though varied widely by file.
